---
title: "OCR_Orange"
author: "Collot, Millard, Ferreira Gomes"
format: html
editor:
  markdown:
    canonical: true
    wrap: 72
---

## Context

## Running Code

We will use the dataset created by the FAO, which lists orange yields by
country and year from 1961 to 2024.

## Orange yield around the world

Found on the **ourworldindata.org**, the data set that we are using,
gives information about the yield on different

## Running Code

When you click the **Render** button a document will be generated that
includes both content and the output of embedded code. You can embed
code like this:

```{r}
#| echo: false
orange <- read.csv(file='orange-yields.csv', sep=',', dec='.')
summary(orange)
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is
displayed).

References : Dataset : Food and Agriculture Organization of the United
Nations (2025) – with major processing by Our World in Data. “Orange
yields – UN FAO” \[dataset\]. Food and Agriculture Organization of the
United Nations, “Production: Crops and livestock products” \[original
data\]. Retrieved September 16, 2026 from
https://archive.ourworldindata.org/20260910-011030/grapher/orange-yields.html
(archived on September 10, 2026).
